---
title: "Phyllosphere microbial associations and plant reproductive success"
---

The phyllosphere plant microbiome is an important component of Plant-Microbe systems. The following data set was was sourced from an article on Dryad. It explores the possibility of adding a synthetic microbial consortium to tomatoes (Solanum lycopersicum) in a greenhouse settings where microbe recruitment could be disrupted.
The added phyllosphere microbial associations was found to improve plant reproductive success.

**Trial 1**

```{r}
#| message: FALSE
#| echo: FALSE

library(ggplot2)
library(tidyverse)
library(plotly)

# Assuming your data reading and ggplot code remains unchanged
file_path <- "C:/Users/LENOVO/Documents/Desktop/projects/phyllosphere-microbiome/data/Trial_1_Greenhouse_Bacterial_Abundance.csv"
df1 <- read_csv(file_path)

# Your ggplot code
p1 <- ggplot(df1, aes(x = Sample_ID, y = TotalAbundance, fill = Treatment, text = TotalAbundance)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Bacterial Abundance in Greenhouse Samples",
       x = "Sample",
       y = "Total Abundance",
       fill = "Treatment") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        panel.grid.minor = element_blank()) +
  scale_fill_manual(values = c("Control" = "#EBFBC4", "PhylloStart" = "#D4C4FB"))

# Convert ggplot object to plotly object
interactive_plot1 <- ggplotly(p1, tooltip = "text")

# Modify the layout to adjust the title position and font size
interactive_plot1 <- interactive_plot1 %>% layout(
  title = list(
    text = "Bacterial Abundance in Greenhouse Samples of <i>Solanum lycopersicum</i>",
    x = 0,  # Adjust the x position to move title to the left (0 is left-aligned)
    xanchor = 'left',  # Anchor the title text to the left
    font = list(size = 20),  # Set the font size to 20 (adjust as needed)
    margin = list(t = 100)
  )
)

# Display the interactive plot
interactive_plot1

```

**Trial 2**

```{r}
#| message: FALSE
#| echo: FALSE

library(ggplot2)
library(dplyr)
library(tidyr)
library(plotly)

# Read the data (replace with your file paths)
df2 <- read.csv("C:/Users/LENOVO/Documents/Desktop/projects/phyllosphere-microbiome/data/Trial_2_Greenhouse_Fruit_Count.csv")
df3 <- read.csv("C:/Users/LENOVO/Documents/Desktop/projects/phyllosphere-microbiome/data/Trial_2_Greenhouse_Fruit_Weights.csv")

# Add a column to each dataframe to indicate the measurement type
df2$Measurement_Type <- "Fruit Count"
df3$Measurement_Type <- "Fruit Weight"

# Rename the y-axis columns for consistency
df2 <- df2 %>% rename(Measurement_Value = Total_Fruit)
df3 <- df3 %>% rename(Measurement_Value = Average_Weight)

# Combine the dataframes
combined_df <- bind_rows(df2, df3)

# Convert Measurement_Type to factor and specify order
combined_df$Measurement_Type <- factor(combined_df$Measurement_Type, levels = c("Fruit Count", "Fruit Weight"))

# Plot using ggplot
p2 <- ggplot(combined_df, aes(x = Bacterial_Treatment, y = Measurement_Value, fill = Bacterial_Treatment)) +
  geom_boxplot() +
  facet_grid(rows = vars(Measurement_Type), cols = vars(Azomite), scales = "free_x", space = "free_x") +
  labs(
    title = "Greenhouse Fruit Count and Weight",
    x = "Bacterial Treatment",
    y = "",
    fill = "Bacterial Treatment"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, margin = margin(b = 20)),  # Add margin to the bottom of the title
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.x = element_text(margin = margin(t = 20)),  # Increase margin between x-axis title and plot
    strip.background = element_rect(colour = "black"),
    strip.text = element_text(size = 12, face = "bold", color = "black")
  ) +
  scale_fill_manual(values = c("Control" = "#EBFBC4", "PhylloStart" = "#D4C4FB"))

# Convert ggplot object to plotly for interactivity
p2 <- ggplotly(p2)

# Modify the layout to adjust the title position, font size, and margin
p2 <- p2 %>% layout(
  title = list(
    text = "Greenhouse Fruit Count and Weight",
    x = 0,  # Adjust the x position to move title to the left (0 is left-aligned)
    xanchor = 'left',  # Anchor the title text to the left
    font = list(size = 20)  # Set the font size to 20 (adjust as needed)
  ),
  margin = list(t = 100),  # Increase top margin (adjust the value as needed)
  legend = list(x = 1.1, y = 0.5)  # Adjust legend position (play with x and y values to move it)
)

# Display the interactive plot
p2
```

**Trial 3**
