---
title: "Trial 3"
execute: 
  message: false
  echo: false
  warning: false
---

Trial 3 combined elements of both greenhouse and field studies to provide a comprehensive understanding of bacterial community dynamics across different environments. 

The plants were inoculated at Weeks 2, 4, and 6, with leaf samples collected at Week 9. The plants were then transferred to a field environment in Week 8, and additional leaf samples were taken again in Week 9. The harvesting occurred in Week 24 to determine the long-term effects of the treatments on fruit production.

```{r}
# Load necessary libraries
library(ggplot2)
library(tidyverse)
library(plotly)

# Load the dataset
file_path <- "C:/Users/LENOVO/Documents/Desktop/projects/phyllosphere-microbiome/data/Trial_3_Greenhouse_and_Field_Bacterial_Abundance.csv"
df4 <- read_csv(file_path)

# Set the factor levels for Treatment
df4$Treatment <- factor(df4$Treatment, levels = c("Control", "PhylloStart Low", "PhylloStart High"))

# Create a ggplot boxplot faceted by Location
p3 <- ggplot(df4, aes(x = Treatment, y = TotalSynComAbundance, fill = Treatment, text = TotalSynComAbundance)) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "Bacterial Abundance in Greenhouse and Field Samples",
       x = NULL,
       y = "Total Microbial Abundance",
       fill = "Bacterial Treatment") +
  theme(panel.grid.minor = element_blank(),
        strip.background = element_rect(color = "black", fill = "white"),  # Add border to facet labels
        strip.text = element_text(face = "bold", size = 14),  # Make the facet labels bold
        axis.text.x = element_text(angle = 45, hjust = 1)) +  # Display x-axis labels diagonally
  scale_fill_manual(values = c("Control" = "#EBFBC4", "PhylloStart Low" = "#FBD4C4", "PhylloStart High" = "#D4C4FB")) +
  facet_wrap(~ Location, ncol = 2)

# Convert ggplot object to plotly object
p3 <- ggplotly(p3, tooltip = "text")

# Modify the layout to adjust the title position and font size, and increase top margin
p3 <- p3 %>% layout(
  title = list(
    text = "Bacterial Abundance in Greenhouse and Field Samples",
    x = 0,  # Adjust the x position to move title to the left (0 is left-aligned)
    xanchor = 'left',  # Anchor the title text to the left
    font = list(size = 20)  # Set the font size to 20 (adjust as needed)
  ),
  margin = list(t = 100)  # Increase top margin to add spacing between the title and the graph
)

# Display the interactive plot
p3
```

PhylloStart does not persist after plants are transplanted to the field.

Different densities of PhylloStart lead to different amounts of leaf colonization for greenhouse plants.

```{r}

library(ggplot2)
library(dplyr)
library(tidyr)
library(plotly)

# Set the file paths for the new CSV files
file_path_count <- "C:/Users/LENOVO/Documents/Desktop/projects/phyllosphere-microbiome/data/Trial_3_Greenhouse_Fruit_Count.csv"
file_path_weight <- "C:/Users/LENOVO/Documents/Desktop/projects/phyllosphere-microbiome/data/Trial_3_Greenhouse_Fruit_Weights.csv"

# Read the data from the uploaded CSV files
df_count <- read.csv(file_path_count)
df_weight <- read.csv(file_path_weight)

# Add a column to each dataframe to indicate the measurement type
df_count$Measurement_Type <- "Fruit Count"
df_weight$Measurement_Type <- "Fruit Weight"

# Rename the y-axis columns for consistency
df_count <- df_count %>% rename(Measurement_Value = Total_Fruit)
df_weight <- df_weight %>% rename(Measurement_Value = Average_Weight)

# Combine the dataframes
combined_df <- bind_rows(df_count, df_weight)

# Convert Measurement_Type to factor and specify order
combined_df$Measurement_Type <- factor(combined_df$Measurement_Type, levels = c("Fruit Count", "Fruit Weight"))

# Convert Bacterial_Treatment to factor and specify order
combined_df$Bacterial_Treatment <- factor(combined_df$Bacterial_Treatment, levels = c("Control", "PhylloStart Low", "PhylloStart High"))

# Plot using ggplot
p4 <- ggplot(combined_df, aes(x = Bacterial_Treatment, y = Measurement_Value, fill = Bacterial_Treatment)) +
  geom_boxplot() +
  facet_grid(rows = vars(Measurement_Type), cols = vars(Azomite), scales = "free_x", space = "free_x",
             labeller = labeller(Azomite = c(`0` = "0g Azomite", `0.5` = "0.5g Azomite", `1` = "1g Azomite", `2` = "2g Azomite", `3` = "3g Azomite"))) +
  labs(
    title = "Greenhouse Fruit Count and Weight",
    x = "Bacterial Treatment",
    y = "",
    fill = "Bacterial Treatment"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, margin = margin(b = 20)),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.x = element_text(margin = margin(t = 20)),
    strip.background = element_rect(colour = "black"),
    strip.text = element_text(size = 12, face = "bold", color = "black")
  ) +
  scale_fill_manual(values = c("Control" = "#EBFBC4", "PhylloStart Low" = "#FBD4C4", "PhylloStart High" = "#D4C4FB"))

# Convert ggplot object to plotly for interactivity
p4 <- ggplotly(p4)

# Modify the layout to adjust the title position, font size, margin, and legend spacing
p4 <- p4 %>% layout(
  title = list(
    text = "Greenhouse Fruit Count and Weight",
    x = 0,
    xanchor = 'left',
    font = list(size = 20)
  ),
  margin = list(t = 100),
  legend = list(
    y = 0.5,
    x = 1.1,
    xanchor = "left"
  )
)

# Display the interactive plot
p4
```

PhylloStart High Density significantly increased fruit production in greenhouse tomatoes.